Unshuffling Permutations

### 2015-09-27 submission.tex
typos

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu'_1)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_2, \nu'_1)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_2, \nu'_1)$-edge $e = (a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_1, nu'_1)-edge}, there exists at least
    one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Furtheremore, since
    there is no $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge}),
    every position in $\nu_1$ is involved either in a
    $(\nu_1, \nu_1)$-edge or in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$
    (otherwise $\mathcal{M}$ would not be containment-free).
    Then it follows that that there is an odd number of $(\nu_1, \nu'_1)$-edges
    in $\mathcal{M}$ since $\mathcal{M}$ is perfect and $|\nu_1| = N_1$ is odd.
    Combining this with the fact that there exists exactly one $(\nu_2, \nu'_1)$-edge
    in $\mathcal{M}$ and $|\nu'_1| = N_1$ is odd,
    we conclude that there exists a position, say $x$, in $\nu'_1$
    that is neither involved in a $(\nu_1, \nu'_1)$-edge nor a $(\nu_1, \nu'_1)$-edge
    nor a $(\nu'_1, \nu'_1)$-edge.
    Write $(x, x')$, $N_1+N_2 < x \leq 2N_1 + N_2$ and $x' > 2N_1 + N_2$, this edge.
    We have $\mu(a) < \mu(x)$ (since $\nu_2$ is below $\nu'_1$)
    and $\mu(a') > \mu(x')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

@@

  Combining the above claims, we conclude that there are
  $k+2$ $(\sigma', \pi')$-edges in $\mathcal{M}$.
  Recall that
  $\sigma' = ((k+1) \; \sigma \; (k+2)) \; [2N_2 + N_4 + 2n + k + 2]$ and that
  $\pi' = ((n+1) \; \pi \; (n+2)) \; [2N_2 + N_4 + n + k + 2]$.
  Then it follows we have
  at least $k$ (possibly $k+1$ or $k+2$) independent $(\sigma', \pi')$-edges
  $(a, a')$ in $\mathcal{M}$ with
  $2N_1 + N_2 + N_3 + 1 < a < 2N_1 + N_2 + N_3 + k + 2$
  and
  $2N_1 + N_2 + N_3 + (k + 2) + 1 < a' < 2N_1 + N_2 + N_3 + (k + 2) + n + 2$.
  Therefore, by our hypothesis about $\mathcal{M}$,
  $\sigma$ occurs as a pattern in $\pi$.
  \qed
\end{proof}

>>>>

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu'_1)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one $(\nu_2, \nu'_1)$-edge in $\mathcal{M}$.
    Suppose now, aiming at a contradiction, that there exists
    exactly one $(\nu_2, \nu'_1)$-edge $e = (a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:(nu_1, nu'_1)-edge}, there exists at least
    one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Furtheremore, since
    there is no $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge}),
    every position in $\nu_1$ is involved either in a
    $(\nu_1, \nu_1)$-edge or in a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$
    (otherwise $\mathcal{M}$ would not be containment-free).
    Then it follows that that there is an odd number of $(\nu_1, \nu'_1)$-edges
    in $\mathcal{M}$ since $\mathcal{M}$ is perfect and $|\nu_1| = N_1$ is odd.
    Combining this with the fact that there exists exactly one $(\nu_2, \nu'_1)$-edge
    in $\mathcal{M}$ and $|\nu'_1| = N_1$ is odd,
    we conclude that there exists a position, say $x$, in $\nu'_1$
    that is neither involved in a $(\nu_1, \nu'_1)$-edge nor in a $(\nu_1, \nu'_1)$-edge
    nor in a $(\nu'_1, \nu'_1)$-edge.
    Write $(x, x')$, $N_1+N_2 < x \leq 2N_1 + N_2$ and $x' > 2N_1 + N_2$, this edge.
    We have $\mu(a) < \mu(x)$ (since $\nu_2$ is below $\nu'_1$)
    and $\mu(a') > \mu(x')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

@@

  Combining the above claims, we conclude that there are
  $k+2$ $(\sigma', \pi')$-edges in $\mathcal{M}$.
  Recall that
  $\sigma' = ((k+1) \; \sigma \; (k+2)) \; [2N_2 + N_4 + 2n + k + 2]$ and that
  $\pi' = ((n+1) \; \pi \; (n+2)) \; [2N_2 + N_4 + n + k + 2]$.
  Then it follows we have
  at least $k$
  %(possibly $k+1$ or $k+2$)
  independent $(\sigma', \pi')$-edges
  $(a, a')$ in $\mathcal{M}$ with
  $2N_1 + N_2 + N_3 + 1 < a < 2N_1 + N_2 + N_3 + k + 2$
  and
  $2N_1 + N_2 + N_3 + (k + 2) + 1 < a' < 2N_1 + N_2 + N_3 + (k + 2) + n + 2$.
  Therefore, by our hypothesis about $\mathcal{M}$,
  $\sigma$ occurs as a pattern in $\pi$.
  \qed
\end{proof}
